---
title: "AI for Research Work Workshop"
output: html_document
---

## Slides

The slides for this workshop are available at the [following link](https://bit.ly/itn_nyu_2024_ai)

```{r echo=FALSE, fig.alt="", fig.link =""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1gFNEhfp4Vh131tpHvdntvpIKKwlJilaNfJLiMTeXvDA/edit#slide=id.g2814c9cb41d_0_5")
```

## Logistical information

### Learner Survey

Please provide information in the [following survey](https://bit.ly/hutch_learner) as this helps us keep you informed of upcoming workshops, and to follow up and see how you are using what you have learned.

```{r echo=FALSE, fig.alt="To provide information for us, please scan this QR code or use the link h t t p s colon forward slash forward slash bit dot l y forward slash hutch underscore learner", fig.link="https://bit.ly/hutch_learner"}
ottrpal::include_slide("https://docs.google.com/presentation/d/1gFNEhfp4Vh131tpHvdntvpIKKwlJilaNfJLiMTeXvDA/edit#slide=id.g2f288e8e9b9_0_0")
```

### Slido

Please also login to slido at [slido.com](https://www.slido.com/) for this workshop for interactive questions throughout.

```{r echo=FALSE, fig.alt="The Slido code for this workshop is 2082139. Please enter the code at slido dot com", fig.link="https://www.slido.com/"}
ottrpal::include_slide("https://docs.google.com/presentation/d/1gFNEhfp4Vh131tpHvdntvpIKKwlJilaNfJLiMTeXvDA/edit#slide=id.g258ce79cf2b_0_204")
```

### Learner Demographic Survey

Please provide information in the [following survey](https://bit.ly/itn_demo) as this helps us gather necessary information we need to report to the NIH for trainings we host.

```{r echo=FALSE, fig.alt="To provide us with necessary reporting information, please use this QR code or follow the link h t t p s colon forward slash forward slash bit dot l y forward slash i t n underscore demo", fig.link="https://bit.ly/itn_demo"}
ottrpal::include_slide("https://docs.google.com/presentation/d/1gFNEhfp4Vh131tpHvdntvpIKKwlJilaNfJLiMTeXvDA/edit#slide=id.g28548f404c3d183_615")
```

## Other Resources

### Relevant (free!) courses

Material for this workshop is adapted from the [AI for Efficient Programming ITN course](https://hutchdatascience.org/AI_for_Efficient_Programming/) and the [AI for Decision Makers ITN course](https://hutchdatascience.org/AI_for_Decision_Makers/introduction-to-avoiding-ai-harm.html). That and our other courses are available for free. See [our website](https://www.itcrtraining.org/courses) for more information. 

```{r echo=FALSE, fig.alt="This table lists the various courses available from the I T N including ones under development that will be available in the future. A I for efficient programming is highlighted becasue this workshop is adapted from that larger course. For more info on and to access any of these courses, visit i t c r training dot org", fig.link="https://www.itcrtraining.org/courses"}
ottrpal::include_slide("https://docs.google.com/presentation/d/1gFNEhfp4Vh131tpHvdntvpIKKwlJilaNfJLiMTeXvDA/edit#slide=id.g2efffa5458b_0_0")
```

### A paper about which chat bot is best for specific tasks

Check out [this paper describing which chat bot is the best for the research task you're interested in](https://www-nature-com.fhcrc.idm.oclc.org/articles/d41586-023-03023-4)